### 2017-04-17 paper2.tex

The temperature of the surface is integral in understanding, predicting, and modeling boundary-layer air temperature patterns, surface energy balances, and, in urban areas, has important implications for human thermal comfort and building energy usage. Urban modification of surface geometry and thermal, radiative, moisture, and aerodynamic properties results in differential surface heating and cooling patterns and strong microscale spatiotemporal variations in urban surface temperature (T\textsubscript{surf}). Integrated up to larger scales, urban areas tend to store and generate more heat relative to non-built surroundings which manifests in elevated T\textsubscript{surf} and T\textsubscript{air} --- a phenomenon termed the urban heat island effect (UHI). To foster a more complete understanding of the effect of urban areas climates across scales, accurate, spatiotemporally continuous and geometrically representative characterization of T\textsubscript{surf} in cities has long been a goal in urban climatology. The proliferation of satellite and aerial thermal infrared (TIR) remote sensing has enabled spatially-extensive characterizations of surface climates at ever improving spatial and spectral resolutions. Such campaigns have elucidated urban T\textsubscript{surf} and surface urban heat island (sUHI) patterns globally at large spatial scales. However, technological improvements in TIR remote sensing have yet to address a three potential sources of error when applied in urban areas:

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=15cm,height=7in,keepaspectratio]{bx_suhi_compare}
	\caption{A comparison of sUHI magnitudes from complete, hemispherical, and nadir remote sensed representations of the Sperrstrasse canyon over the IOP. Each plot includes mean sUHI, as well case days representing sUHI under clear sky and clouded sky conditions.}
	\label{bx_suhi_compare}
\end{figure}

@@

\begin{table}[H]
	\centering
	\caption{A summary of the relationship between sUHI, meteorological variables, and clUHI.}
	\label{meteo_cont}
	\begin{tabular}{lc}
		\toprule 
		An increase in $x$, has a/an... & $y$ effect on sUHI magnitude. \\
		\midrule
		$\Delta$T\textsubscript{hem, r - air} &\textit{increasing} \\
		&\\
		T\textsubscript{hem, r} & \textit{increasing} \\
		&\\
		T\textsubscript{air} & \textit{increasing} \\

		&\\
		Incoming solar radiation & \textit{increasing}  \\
		& \\
		& \\
		Water vapor content & \textit{negligible} \\
		&\\
		Wind velocity &\textit{decreasing} \\
		&\\
		clUHI &\textit{increasing} \\
		\bottomrule
	\end{tabular} 
\end{table}

>>>>

The temperature of the surface is integral in understanding, predicting, and modeling boundary-layer air temperature patterns, surface energy balances, and, in urban areas, has important implications for human thermal comfort and building energy usage. Urban modification of surface geometry and thermal, radiative, moisture, and aerodynamic properties results in differential surface heating and cooling patterns and strong microscale spatiotemporal variations in urban surface temperature (T\textsubscript{surf}). Integrated up to larger scales, urban areas tend to store and generate more heat relative to non-built surroundings which manifests in elevated T\textsubscript{surf} and T\textsubscript{air} a phenomenon termed the urban heat island effect (UHI). To foster a more complete understanding of the effect of urban areas climates across scales, accurate, spatiotemporally continuous and geometrically representative characterization of T\textsubscript{surf} in cities has long been a goal in urban climatology. The proliferation of satellite and aerial thermal infrared (TIR) remote sensing has enabled spatially-extensive characterizations of surface climates at ever improving spatial and spectral resolutions. Such campaigns have elucidated urban T\textsubscript{surf} and surface urban heat island (sUHI) patterns globally at large spatial scales. However, technological improvements in TIR remote sensing have yet to address a three potential sources of error when applied in urban areas:

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=15cm,height=7in,keepaspectratio]{bxsuhi1}
	\caption{A comparison of sUHI magnitudes from complete, hemispherical, and nadir remote sensed representations of the Sperrstrasse canyon over the IOP. Each plot includes mean sUHI, as well case days representing sUHI under clear sky and clouded sky conditions.}
	\label{bx_suhi_compare}
\end{figure}

@@

\begin{table}[H]
	\centering
	\caption{A summary of the relationship between sUHI, meteorological variables, and clUHI.}
	\label{meteo_cont}
	\begin{tabular}{lc}
		\toprule 
		An increase in $x$, has a/an... & $y$ effect on sUHI magnitude. \\
		\midrule
		$\Delta$T\textsubscript{hem, r - air} &\textit{increasing} \\
		&\\
		T\textsubscript{hem, r} & \textit{increasing} \\
		&\\
		T\textsubscript{air} & \textit{increasing} \\
		&\\
		Incoming solar radiation & \textit{increasing}  \\
		& \\
		Water vapor content & \textit{negligible} \\
		&\\
		Wind velocity &\textit{decreasing} \\
		&\\
		clUHI &\textit{increasing} \\
		\bottomrule
	\end{tabular} 
\end{table}
